Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2022-04-18 paper-correlations.tex
Add plots for five functions

\section{Examples and applications}
\label{exasec}
Text

>>>>

\section{Examples and applications}
\label{exasec}
After the verification of our computational approach based on analytical
solution we can apply our algorithms to evaluate correlation functions for
different porous media images, including real XCT and SEM images.

For demonstration purposes, we computed correlation functions for images of
sandstone found on Digital Rocks Portal \cite{DigitalRocks} all of which have
dimensions $1000 \times 1000$. The result can be seen on \cref{fig:real-data}.

\begin{figure*}[t]
  \centering
  \subfigure[$S_2^{(void)}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-s2void.png}
    \label{fig:real-s2}}
  \hfill
  \subfigure[$L_2^{(void)}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-l2void.png}
    \label{fig:real-l2}}
  \subfigure[$C_2^{(void)}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-c2void.png}
    \label{fig:real-c2}}
  \vskip\baselineskip
  \subfigure[$F_{ss}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-ss.png}
    \label{fig:real-ss}}
  \subfigure[$F_{sv}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-sv.png}
    \label{fig:real-sv}}
  \caption[]{Plots of correlation functions for images of sandstones.}
  \label{fig:real-data}
\end{figure*}
